\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2015-09-21 paper.tex
update
updated title and some minor stuff
update in title
addressed last of Cheng's feedback

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)}

@@

Our methodology has been applied to three production distributed storage systems in the Microsoft Azure platform. In the process, numerous bugs were identified, reproduced, confirmed and fixed. These bugs required a subtle combination of concurrency and failures, making them extremely difficult to find with conventional testing techniques. An important advantage of our approach is that a bug is uncovered in a small setting and witnessed by a full system trace, which dramatically increases the productivity of debugging.

>>>>

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)}
%\title{\Large \bf Uncovering Distributed Storage System Bugs during\\Testing (not in Production!)}

@@

Our methodology has been applied to three distributed storage systems in the Microsoft Azure cloud computing platform. In the process, numerous bugs were identified, reproduced, confirmed and fixed. These bugs required a subtle combination of concurrency and failures, making them extremely difficult to find with conventional testing techniques. An important advantage of our approach is that a bug is uncovered in a small setting and witnessed by a full system trace, which dramatically increases the productivity of debugging.

### 2015-09-21 related.tex
addressed last of Cheng's feedback

Tools such as CrystalBall~\cite{yabandeh2009crystalball} and \textsc{DeMeter}~\cite{guo2011practical} employ techniques based on dynamic partial order reduction~\cite{lauterburg2010evaluating} to reduce the exploration state-space. The SAMC~\cite{leesatapornwongsa2014samc} model checker offers a way of incorporating application-specific information during systematic testing, but the focus is still on reducing the set of interleavings. Although the SAMC authors claim that their tool is orders of magnitude faster than previous testing techniques, they mention that their ``extensive evaluation exercised more than 100,000 executions and used approximately 48 full machine days''~\cite{leesatapornwongsa2014samc}. \psharp is able to explore a similar number of iterations in a matter of hours, and find serious bugs in seconds (see \S\ref{sec:eval}). However, we do \emph{not} claim that \psharp is faster; as aforementioned, we focus on compositional testing, whereas prior work typically focuses on testing an entire system. We are just trying to solve a similar problem at a very different level.

>>>>

Tools such as CrystalBall~\cite{yabandeh2009crystalball} and \textsc{DeMeter}~\cite{guo2011practical} employ techniques based on dynamic partial order reduction~\cite{lauterburg2010evaluating} to reduce the exploration state-space. The SAMC~\cite{leesatapornwongsa2014samc} model checker offers a way of incorporating application-specific information during systematic testing, but the focus is still on reducing the set of possible interleavings. Although SAMC is orders of magnitude faster than previous testing techniques, the authors mention that their ``extensive evaluation exercised more than 100,000 executions and used approximately 48 full machine days''~\cite{leesatapornwongsa2014samc}. \psharp is able to explore a similar number of iterations in a matter of hours, and find serious bugs in seconds (see \S\ref{sec:eval}). However, we do \emph{not} claim that \psharp is faster; as aforementioned, we focus on compositional testing, whereas prior work typically focuses on testing an entire system. We are just trying to solve a similar problem at a very different level.
